SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-18 paper/experiments.tex
more changes
many more changes

\begin{table}[t]
\centering
% \def\arraystretch{1.6}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    {\multirow{2}{*}{\textbf{Version}}}  & 
    \multicolumn{2}{c|}{\textbf{Constraints}} & 
    \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
   \cline{2-5}
   &  \textbf{Rest} & \textbf{Activity} & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\ \hline

@@

In Table~\ref{tab:qf-grabh}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM.
%
We have compared our performance with the performance of our earlier 
CBMC based implementation.
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Hence with the use of this novel encoding, we are able to scale the
system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of ten compartments.
%
This additional scalability can provide us leverage to ask for related
open questions that were not previously possible, for example, what is
the minimum number of molecules required to satisfy the vesicular
traffic system in eukaryotes.
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.

>>>>

\begin{table}[t]
\centering
% \def\arraystretch{1.6}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    {\multirow{2}{*}{\textbf{Variant}}}  & 
    \multicolumn{2}{c|}{\textbf{Constraints}} & 
    \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
   \cline{2-5}
   &  \textbf{Rest} & \textbf{Activity} & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\ \hline

@@

In Table~\ref{tab:qf-grabh}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM.
%
We have compared our performance with the performance of our earlier 
CBMC based implementation.
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Hence with the use of this novel encoding, we are able to scale the
system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of ten compartments.
%
\ankit{
This additional scalability can provide us leverage to ask for related
open questions that were not previously possible, for example, what is
the minimum number of molecules required to satisfy the vesicular
traffic system in eukaryotes.}
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.
